Reading Notes

### 2020-05-29 paper.tex
added new refs from arthi's paper!
reading more arthis paper--very good but LOGN

\cite{Gartner2019a}
Somehow didn't add this!
University of delaware. There is a Jankowski/Marsh image in Fig 1!
OMG I just realised this is Arthi from the MoSDeF calls. :D No wonder this paper is so approachable!! 
Atomistic structures, not always more accurate, can't compute polymer chain level rearrangement
CG -- chemists might not like them but physicists do
atomistic simulations are good when you already know the chain configuration at a state point. Atomistic FF are still tailored to fit the properties of specific systems. got distracted today... will continue with II.B tomorrow
OK back to it
CG - intermediate resolution (group of atoms within a monomer), CG monomer (whole monomer), mesoscale CG model (group of monomers on the length of a Kuhn segment or the whole chain.
Finer models are parameterized to represent specific chemistries while coarse models are more generic. finer models can be parameterized with IBI for structure or force matching or relative entropy matching. the level of coarseness should depend on what features you want to examine.
MARTINI - generic model 3-5 heavy atoms are grouped together each bead is assigned polar/apolar/donor/acceptor etc based on the chemistry/connectivity.
soft potentials can be used for CG beads like DPD -- can have unphysically high compressibility
!!! Systematic coarse graining approaches refs (87,91,269-273)
start reading tomorrow at pt III
\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}

>>>>

\cite{Gartner2019a}
Somehow didn't add this!
University of delaware. There is a Jankowski/Marsh image in Fig 1!
OMG I just realised this is Arthi from the MoSDeF calls. :D No wonder this paper is so approachable!! 
Atomistic structures, not always more accurate, can't compute polymer chain level rearrangement
CG -- chemists might not like them but physicists do
atomistic simulations are good when you already know the chain configuration at a state point. Atomistic FF are still tailored to fit the properties of specific systems. got distracted today... will continue with II.B tomorrow
OK back to it
CG - intermediate resolution (group of atoms within a monomer), CG monomer (whole monomer), mesoscale CG model (group of monomers on the length of a Kuhn segment or the whole chain.
Finer models are parameterized to represent specific chemistries while coarse models are more generic. finer models can be parameterized with IBI for structure or force matching or relative entropy matching. the level of coarseness should depend on what features you want to examine.
MARTINI - generic model 3-5 heavy atoms are grouped together each bead is assigned polar/apolar/donor/acceptor etc based on the chemistry/connectivity.
soft potentials can be used for CG beads like DPD -- can have unphysically high compressibility
!!! Systematic coarse graining approaches refs (87,91,269-273)
start reading tomorrow at pt III

simulation method (MC or MD) three steps
1. create/initialize system
2. equilibrate
3. sample
all steps should avoid bias.
also choose ensemble, thermostat, barostat... choose for what you want to know. e.g. phase behavior - GCMC or GEMC phase coexistence with bead insertion/deletion. don't have to model the interface. Ref 308 is a GEMD method devolped by Arthi's group!

Size: big enough that you can observe the phenomena you looking for. Calculating Flory-Huggins or polymer-polymer second virial coeff require long length scales. phase separations must also be larger than the length scale of the concentration fluctuations. However if interested indilute-soln properties like chain configuration or scaling laws--single chain even can be appropriate.
finite size effects emerge from self interaction with the periodic image and limited size of box/system. smaller size can lead to pressure and stress fluctuation preventing calculation of mechanical properties.
good rule of thumb -- box length to radius of gyration should be L/Rg >= 5.

initialization: random initialization might be fine if system is isotropic but not at high density. A procedure to initialize high density CG polymer melts which uses MC with no intrachain moves and soft MD is described.
an important metric for chain configuration is mean squared internal distance (measure of atoms or beads separated by n bonds along the chain). shows perturbations in internal chain not shown by the radius of gyration or end to end distance.
We use a shrink-step, but that isn't mentioned here...

Equilibration:
relaxation in chain configuration is slow compared to relaxation of chain level metrics (like the mean squared interanl distance) or check MSD of CoM of polymer chains -- if they diffuse nultiples of Rg over equilibration, the system is relaxed. annealing processes (change T and P (also V???)) can help equillibrate. also mimic experiment.
Start again at p.11 Sampling
\cite{Muller-Plathe2002}
\cite{Ayton2007a}
\cite{Peter2009c}
\cite{Baschnagel2000}
\cite{Brini2013}
\cite{Murtola2009a}
\cite{Peter2009d}

\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
